\SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2022-06-06 response-to-reviewer-comments.tex

\documentclass{article} % This command is used to set the type of document you are working on such as an article, book, or presenation

\usepackage{geometry} % This package allows the editing of the page layout
\usepackage{amsmath}  % This package allows the use of a large range of mathematical formula, commands, and symbols
\usepackage{graphicx}  % This package allows the importing of images

\title{Response to reviewer comments}
\author{Logan Bishop-Van Horn}
\date{\today}

\begin{document}
\maketitle

\section{Reviewer 1}

\begin{itemize}
    \item{
    {\bf Reviewer comment:} ``The manuscript is well written and the work is of interest to the applied superconductivity community.''

    {\bf Author response:} We are glad that the reviewer found the paper to be well written, and we agree that the software and manuscript will be valuable to the applied superconductivity community.
    }
    \item{
    {\bf Reviewer comment:} ``The software works, although the implementation is a bit slower and more memory hungry than commercial or closed-source tools.''

    {\bf Author response:} It is true that the software favors portability and simplicity of implementation over raw performance, likely making it less efficient than some commercial or closed-source tools. We do not see SuperScreen as a competitor to or replacement for superconducting electronic design automation (EDA) and inductance extraction tools such as InductEx and FastHenry. Rather, we see SuperScreen as a complementary research tool for modeling experiments involving 2D superconductors and mesoscopic superconducting devices, as opposed to designing superconducting integrated circuits. 
    }
    \item{
    {\bf Reviewer comment:} ``The reference to [16] for a review of inductance extraction is a bit old -- newer tools and methods and publications exist.''

    {\bf Author response:} Reference 16 is indeed a bit old. We have added more recent references
    }
    \item{
    {\bf Reviewer comment:} ``P.4, Left Column, Line 53: `though' should be `through'.''

    {\bf Author response:} Thank you for the careful reading and for catching this typo. The typo has been fixed in the revised version of the manuscript.
    }
\end{itemize}

\section{Reviewer 2}
\begin{itemize}
    \item{
    {\bf Reviewer comment:} ``Highlights and graphical abstract could be provided.''

    {\bf Author response:}
    }
    \item{
    {\bf Reviewer comment:} ``As there are many other similar works available, please provide a strong literature survey.''

    {\bf Author response:}
    }
    \item{
    {\bf Reviewer comment:} ``A comparison of the work with state of the art is necessary.''

    {\bf Author response:}
    }
\end{itemize}

\end{document}

### 2022-06-06 main.tex
Updates from Overleaf

There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Jackman2016-mf}. However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls}. \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.

@@

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda$ obey the second London equation:
$\vec{H}(\vec{r})-\lambda^2\vec{\nabla}\times\vec{j}(\vec{r})=$, where
$\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$ is the 3D gradient operator. The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to
\begin{equation}
    \label{eq:london}
    \vec{H}(x, y)=-\Lambda\vec{\nabla}\times\vec{J}(x, y)\\
\end{equation}
where $\Lambda=\lambda^2/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and now $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$.

@@

The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see Ref.~\cite{Brandt2005-wj} for more interesting properties of the stream function). We can rewrite Eq.~\ref{eq:london}, which gives the magnetic field inside of a 2D film, in terms of $g$:
\begin{align}
    \label{eq:london_stream}
    \begin{split}
        \vec{H}(x, y) &= -\Lambda\left[\nabla\times\vec{J}(x, y)\right]\\
        &= -\Lambda\left[\vec{\nabla}\times\left(\vec{\nabla}\times(g\hat{z})\right)\right]\\
        &= -\Lambda\left[\vec{\nabla}(\vec{\nabla}\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
        &=\Lambda\nabla^2g(x,y)\hat{z},
    \end{split}
\end{align}
where $\nabla^2=\vec{\nabla}\cdot\vec{\nabla}$ is the Laplace operator. (The last line follows from the fact that $\vec{\nabla}\cdot\left[g(x,y)\hat{z}\right] = 0$.) From Ampere's Law, the three components of the magnetic field $\vec{H}(\vec{r})$ at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
\begin{align}
    \label{eq:field_from_kernel}
    \begin{split}
        H_x(\vec{r}) &= \int_F Q_x(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_y(\vec{r}) &= \int_F Q_y(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_z(\vec{r}) &= H_{z,\,\mathrm{applied}}(\vec{r})
        + \int_F Q_z(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'.  
    \end{split}
\end{align}

@@

Convergence can be quantified by, for example, calculating the total magnetic flux though all films and holes in the model at the end of each iteration. In general, the more layers there are in a structure the more iterations are  required to reach a given level of convergence.

@@

In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:Heff_sub}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
(Delaunay) mesh, consisting of $p$ points (or vertices)
which together form $t$ triangles. Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
denotes matrix multiplication, with $(\mathbf{A}\mathbf{B})_{ij}=\sum_{k=1}^\ell A_{ik}B_{kj}$
($\ell$ being the number of columns in $\mathbf{A}$ and the number of rows in $\mathbf{B}$). Column vectors are treated as matrices with $\ell$ rows and 1 column. We denote element-wise multiplication with a lower dot, $(\mathbf{A}.\mathbf{B})_{ij}=A_{ij}B_{ij}$, and $\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.

@@

The $p\times p$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\pvec{r}')$ for all points lying in the plane of the film, and the $p\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$. Both $\mathbf{Q}$ and $\mathbf{w}$ are solely determined by the geometry of the mesh, so they only need to be computed once for a given device. $\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $p\times 1$ vectors, with each row representing the value of the quantity at the
corresponding vertex in the mesh. The vector $\mathbf{w}$ is equal to the diagonal of the ``lumped mass matrix'' $\mathbf{M}$: $w_i=M_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$. The kernel matrix $\mathbf{Q}$ is given by
\begin{equation}
    \label{eq:kernel_matrix}
    Q_{ij} = (\delta_{ij}-1)q_{ij}
    + \delta_{ij}\frac{1}{w_{j}}\left(C_i + \sum_{l\neq i}q_{il}w_{l}\right),
\end{equation}
where $q_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\pvec{r}')$ cf. Eq.~\ref{eq:kernels}),
and $\delta_{ij}$ is the Kronecker delta function. The diagonal terms involving the $p\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{Brandt2005-wj} for more details), and $\mathbf{C}$ is given by
\begin{equation}
    \label{eq:C_vector}
    C_i = \frac{1}{4\pi}\sum_{p,q=\pm1}\sqrt{[\Delta x - p(x_i-\bar{x})]^{-2} + [\Delta y - q(y_i-\bar{y})]^{-2}},
\end{equation}
where $\Delta x=(x_\mathrm{max}-x_\mathrm{min})/2$ and $\Delta y=(y_\mathrm{max}-y_\mathrm{min})/2$ are half the side lengths of a rectangle bounding the modeled film and $(\bar{x}, \bar{y})$ are the coordinates of the center of the rectangle.

@@

Each layer can contain one or more superconducting \inline{films} which may have one or more \inline{holes} in them. Films and holes are represented by instances of the \inline{superscreen.Polygon} class. All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film. \inline{Polygons} can be constructed and combined using set-theoretic operations. Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$. Note that \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package~\cite{shapely}.

@@

# Define the device geometry.
length_units = "um"
ro = 3  # outer radius
ri = 1  # inner radius
slit_width = 0.25
Lambda = 1  # effective penetration depth
# circle() and box() generate arrays of polygon (x, y) coordinates.
ring = circle(ro)
hole = circle(ri)
slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
# Define the Polygon representing the superconductor.
layer = sc.Layer("base", Lambda=Lambda)
film = sc.Polygon.from_difference(
    [ring, slit, hole], name="ring_with_slit", layer="base"
)
bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
# Create a Device and generate and plot the computational mesh.
device = sc.Device(
    film.name,
    layers=[layer],
    films=[film],
    abstract_regions=[bounding_box],
    length_units=length_units,
)
device.make_mesh(min_points=3500, optimesh_steps=None)
device.plot(mesh=True)
# Calculate the device's response to a uniform applied field.
applied_field = sc.sources.ConstantField(10)
solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
# Visualize the solution.
# Plot the current density evaluated at each layer in the Device.
solution.plot_currents()
# Plot the magnetic field evaluated at each layer in the Device.
solution.plot_fields()
# Plot the field evaluated at any points in space.
solution.plot_field_at_positions(device.points, zs=0.5)
\end{minted}
\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define the device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field and/or trapped flux, and 4) visualize the results.}
\label{code:device}
\end{code}

\subsection{Solvers}
\label{section:overview:solvers}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $1\,\mathrm{mT}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$. ({\bf a}) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. ({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. ({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. ({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
    \label{fig:ring-with-slit}
\end{figure*}

@@

While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values. For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value. This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function. For $N_h=1$, it is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}. For $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters. Code Block~\ref{code:fluxoid} demonstrates how to model a device with one or more holes, each in the $n=0$ fluxoid state, subject to a uniform applied field, and Figure~\ref{fig:fluxoid} shows the field and current distributions for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole. The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}. It is important to note that while \SuperScreen can calculate the field and current distributions for a given fluxoid state, the model does not capture transitions between fluxoid states.

@@

The self-inductance $L$ of a 2D circular ring with inner radius $a$ and outer radius $b$ (see inset of Figure~\ref{fig:inductance}) has been used as an informal benchmark for superconducting inductance calculations. For a ring with effective penetration depth $\Lambda = 0$, it has been shown analytically that $L\to 2\mu_0 a$ in the limit $a/b\to 0$~\cite{Ketchen2012-mb, Babaei_Brojeny2003-la}. Khapaev calculated the inductance for $\Lambda = 0$ as a function of $a/b$~\cite{Khapaev1997-kw}, and Brandt and Clem calculated the inductance as a function of both $\Lambda$ and $a / b$~\cite{Brandt2004-ew}. Figure~\ref{fig:inductance} shows a comparison between these previous numerical results and the results from \SuperScreen. Note that the models used by Brandt and Clem (solid lines) and by the LCR2D software (blue diamonds) require a circularly symmetric superconducting film, whereas \SuperScreen (filled circles) and 3D-MLSI~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw} (blue squares) support arbitrary 2D geometry.

@@

There are several important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt2004-ew,Brandt2005-wj}. First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ large compared to the film thickness $d$, such that the current density is approximately constant along the thickness of the film. There are cases where the model reproduces experimental results despite violation of this condition (e.g. the calculations and in Refs.~\cite{Kirtley2016-zz,Kirtley2016-gt} and Section~\ref{section:examples:scanning-squid}), but care must be taking in interpreting results in these cases. Second, the model assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device. Third, \SuperScreen does not support ``terminal currents,'' i.e. currents flowing in one terminal of a device and out another terminal. This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux. Terminal currents can, however, be included in stream function-based models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}. An extension to the model described above that treats the magnetic response of a superconducting ring interrupted by two Josephson junctions (i.e. a SQUID) with trapped vortices and terminal currents is given in Ref.~\cite{Clem2005-ye}. Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size (see \ref{appendix:numerics}).

>>>>

There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev,  Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}. However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls, Tolpygo2021-jz}. \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.

@@

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda$ obey the second London equation:
$\vec{H}(\vec{r})-\lambda^2\vec{\nabla}\times\vec{j}(\vec{r})=$, where
$\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$ is the 3D gradient operator. The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to
\begin{equation}
    \label{eq:london}
    \vec{H}(x, y)=-\Lambda\vec{\nabla}\times\vec{J}(x, y)\\
\end{equation}
where $\Lambda=\lambda^2/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$ is now the 2D gradient operator.

@@

The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see Ref.~\cite{Brandt2005-wj} for more interesting properties of the stream function). We can rewrite Eq.~\ref{eq:london}, which gives the magnetic field inside of a 2D film, in terms of $g$:
% \begin{align}
%     \label{eq:london_stream}
%     \begin{split}
%         \vec{H}(x, y) &= -\Lambda\left[\nabla\times\vec{J}(x, y)\right]\\
%         &= -\Lambda\left[\nabla\times\left(\nabla\times(g\hat{z})\right)\right]\\
%         &= -\Lambda\left[\nabla(\nabla\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
%         &=\Lambda\nabla^2g(x,y)\hat{z},
%     \end{split}
% \end{align}
\begin{align}
    \label{eq:london_stream}
    \begin{split}
        \vec{H}(x, y) &= -\Lambda\left[\nabla\times\vec{J}(x, y)\right]\\
        &= -\Lambda\left[\vec{\nabla}\times\left(\vec{\nabla}\times(g\hat{z})\right)\right]\\
        &= -\Lambda\left[\vec{\nabla}(\vec{\nabla}\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
        &=\Lambda\nabla^2g(x,y)\hat{z},
    \end{split}
\end{align}
where $\nabla^2=\vec{\nabla}\cdot\vec{\nabla}$ is the Laplace operator. (The last line follows from the fact that $\vec{\nabla}\cdot\left[g(x,y)\hat{z}\right] = 0$.) From Ampere's Law, the three components of the magnetic field $\vec{H}(\vec{r})$ at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
\begin{align}
    \label{eq:field_from_kernel}
    \begin{split}
        H_x(\vec{r}) &= \int_F Q_x(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_y(\vec{r}) &= \int_F Q_y(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_z(\vec{r}) &= H_{z,\,\mathrm{applied}}(\vec{r})
        + \int_F Q_z(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'.  
    \end{split}
\end{align}

@@

Convergence can be quantified by, for example, calculating the total magnetic flux through all films and holes in the model at the end of each iteration. In general, the more layers there are in a structure the more iterations are  required to reach a given level of convergence.

@@

In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:Heff_sub}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
(Delaunay) mesh, consisting of $p$ points (or vertices)
which together form $t$ triangles. Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
denotes matrix multiplication, with $(\mathbf{A}\mathbf{B})_{ij}=\sum_{k=1}^\ell A_{ik}B_{kj}$
($\ell$ being the number of columns in $\mathbf{A}$ and the number of rows in $\mathbf{B}$). Column vectors are treated as matrices with $\ell$ rows and 1 column. On the other hand, we denote element-wise multiplication with a lower dot: $(\mathbf{A}.\mathbf{B})_{ij}=A_{ij}B_{ij}$ for two matrices
and $(\mathbf{A}.\mathbf{v})_{ij}=(\mathbf{v}.\mathbf{A})_{ij}=A_{ij}v_{i}$ for a matrix $\mathbf{A}$ and a column vector $\mathbf{v}$. $\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.

@@

The $p\times p$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\pvec{r}')$ for all points lying in the plane of the film, and the $p\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$. Both $\mathbf{Q}$ and $\mathbf{w}$ are solely determined by the geometry of the mesh, so they only need to be computed once for a given device. $\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $p\times 1$ vectors, with each row representing the value of the quantity at the
corresponding vertex in the mesh. The vector $\mathbf{w}$ is equal to the diagonal of the ``lumped mass matrix'' $\mathbf{M}$: $w_i=M_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$. The kernel matrix $\mathbf{Q}$ is given by
\begin{equation}
    \label{eq:kernel_matrix}
    Q_{ij} = (\delta_{ij}-1)q_{ij}
    + \delta_{ij}\frac{1}{w_{ij}}\left(C_i + \sum_{l\neq i}q_{il}w_{il}\right),
\end{equation}
where $q_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\pvec{r}')$ cf. Eq.~\ref{eq:kernels}),
and $\delta_{ij}$ is the Kronecker delta function. The diagonal terms involving the $p\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{Brandt2005-wj} for more details), and $\mathbf{C}$ is given by
\begin{equation}
    \label{eq:C_vector}
    C_i = \frac{1}{4\pi}\sum_{p,q=\pm1}\sqrt{[\Delta x - p(x_i-\bar{x})]^{-2} + [\Delta y - q(y_i-\bar{y})]^{-2}},
\end{equation}
where $\Delta x=(x_\mathrm{max}-x_\mathrm{min})/2$ and $\Delta y=(y_\mathrm{max}-y_\mathrm{min})/2$ are half the side lengths of a rectangle bounding the modeled film and $(\bar{x}, \bar{y})$ are the coordinates of the center of the rectangle.

@@

Each layer can contain one or more superconducting \inline{films} which may have one or more \inline{holes} in them. Films and holes are represented by instances of the \inline{superscreen.Polygon} class. All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film. \inline{Polygons} can constructed and combined using set-theoretic operations. Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$. Note that \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package~\cite{shapely}.

@@

# Define the device geometry.
length_units = "um"
ro = 3  # outer radius
ri = 1  # inner radius
slit_width = 0.25
Lambda = 1  # effective penetration depth
# circle() and box() generate arrays of polygon (x, y) coordinates.
ring = circle(ro)
hole = circle(ri)
slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
# Define the Polygon representing the superconductor.
layer = sc.Layer("base", Lambda=Lambda)
film = sc.Polygon.from_difference(
    [ring, slit, hole], name="ring_with_slit", layer="base"
)
bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
# Create a Device and generate and plot the computational mesh.
device = sc.Device(
    film.name,
    layers=[layer],
    films=[film],
    abstract_regions=[bounding_box],
    length_units=length_units,
)
device.make_mesh(min_points=3500, optimesh_steps=None)
device.plot(mesh=True)
# Calculate the device's response to a uniform applied field.
applied_field = sc.sources.ConstantField(10)
solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
# Visualize the solution.
# Plot the current density evaluated at each layer in the Device.
solution.plot_currents()
# Plot the magnetic field evaluated at each layer in the Device.
solution.plot_fields()
# Plot the field evaluated at any points in space.
solution.plot_field_at_positions(device.points, zs=0.5)
\end{minted}
\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define the device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field and/or trapped flux, and 4) visualize the results.}
\label{code:device}
\end{code}

\subsection{Solvers}
\label{section:overview:solvers}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$. ({\bf a}) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. ({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. ({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. ({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
    \label{fig:ring-with-slit}
\end{figure*}

@@

While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values. For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value. This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function. For $N_h=1$, it is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}. For $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters. Code Block~\ref{code:fluxoid} demonstrates how to model a device with one or more holes, each in the $n=0$ fluxoid state, subject to a uniform applied field, and Figure~\ref{fig:fluxoid} shows the field and current distributions for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole. The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}. It is important to note that while \SuperScreen can calculate the field and current distributions or a given fluxoid state, the model does not capture transitions between fluxoid states.

@@

The self-inductance $L$ of a 2D circular ring with inner radius $a$ and outer radius $b$ (see inset of Figure~\ref{fig:inductance}) has been used as an informal benchmark for superconducting inductance calculations. For a ring with effective penetration depth $\Lambda = 0$, it has been shown analytically that $L\to 2\mu_0 a$ in the limit $a/b\to 0$~\cite{Ketchen2012-mb, Babaei_Brojeny2003-la}. Khapaev calculated the inductance for $\Lambda = 0$ as a function of $a/b$~\cite{Khapaev1997-kw}, and Brandt and Clem calculated the inductance as a function of both $\Lambda$ and $a / b$~\cite{Brandt2004-ew}. Figure~\ref{fig:inductance} shows a comparison between these previous numerical results and the results from \SuperScreen. Note that the models used by Brandt and Clem (solid lines) and by the LCR2D software (blue diamonds) require a circularly symmetric superconducting film, whereas \SuperScreen (filled circles) and 3D-MLSI~\cite{Khapaev1997-kw} (blue squares) support arbitrary 2D geometry.

@@

There are several important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt2004-ew,Brandt2005-wj}. First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ large compared to the film thickness $d$, such that the current density is approximately constant along the thickness of the film. There are cases where the model reproduces experimental results despite violation of this condition (e.g. the calculations and in Refs.~\cite{Kirtley2016-zz,Kirtley2016-gt} and Section~\ref{section:examples:scanning-squid}), but care must be taking in interpreting results in these cases. Second, the model assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device. Third, \SuperScreen does not support ``terminal currents,'' i.e. currents flowing in one terminal of a device and out another terminal. This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux. Terminal currents can, however, be included in stream function-based models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw, Khapaev2002-ev, Muller2021-ci}. An extension to the model described above that treats the magnetic response of a superconducting ring interrupted by two Josephson junctions (i.e. a SQUID) with trapped vortices and terminal currents is given in Ref.~\cite{Clem2005-ye}. Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size (see \ref{appendix:numerics}).
